\section{Related Work}

Adobe Story \cite{adobestory2016}, FinalDraft \cite{finaldraft2016} and Celtx \cite{celtx2016} are examples of professional software dedicated to script writing. They support collaboration, automatic formatting, navigation and planning for future production, but they treat the script as a text document that is essentially separate from the recordings. In fact, in our formative interviews of lay and professional audio producers, we found that many of them use general-purpose document editors like Google Docs \cite{googledocs2016} or Microsoft Word \cite{microsoftword2016} to prepare their scripts.

At the recording and editing stage, many users rely on commercial digital audio workstations (DAWs), like Adobe Audition \cite{adobeaudition2016}, Avid ProTools \cite{avidprotools}, GarageBand \cite{garageband} and Audacity \cite{audacity}. Video editing software such as Adobe Premiere \cite{premier} or ScreenFlow \cite{screenflow} are also commonly used. These tools allow users to edit audio by manipulating waveforms in a multi-track timeline interface. They also provide a wide variety of low-level signal processing functions. However, since they are designed to serve as general-purpose audio production systems, they include many features that are not directly relevant for creating audio narratives whose main content is speech. Hindenburg Systems \cite{hindenburg} develops tools that are specifically targeted for audio narratives. Still, they are primarily concerned only with the audio and they do not deal with the script directly.   

Recently, several researchers have explored using audio transcripts to support text-based navigation and editing of audio. Whittaker and Amento \cite{whittaker2004semantic} demonstrate that users prefer editing voicemail through its transcript instead of its waveform. Inspired by similar intuition, Casares et al. \cite{casares2002simplifying} and Berthouzoz et al. \cite{berthouzoz2012tools} enable video navigation and editing through time-aligned transcripts. Rubin et al. \cite{rubin2013content} extend this approach to audio narratives and propagate edits in the transcript text to the corresponding speech track. These systems all focus on editing pre-recorded audio via its transcript, whereas we also consider how script
edits influence the recording process and how audio edits
also evolve the script. 
%  \VTODO{Hm. That's not entirely true. I think these systems tend to rely on an input transcription of the recording, but that resulting transcript can be edited. Maybe we should say that these systems focus solely on editing recorded audio via text, whereas we also consider how script edits influence the recording process and how audio edits should evolve the script. Or something like that.} 
\VREV{\textit{NarrationCoach} developed by Rubin et al.} \cite{rubin2015capture} \VREV{also uses ASR to align speech recordings with an input script. However, its focus, improving speech performance at recording time, is very different from ours. We focus on facilitating the back-and-forth workflow between script writing and speech recording.}
Our work also takes advantage of text-based navigation and editing, but unlike these systems, we support a dynamic workflow where both the audio recordings and the underlying script can be continuously  updated.      
